Blocking-resistant communication\\through domain fronting

### 2014-07-25 docs/meek.tex
Minor revisions.

To our knowledge,
the earliest application of domain fronting to circumvention
was by GoAgent~\cite{goagent},
a tool based on App Engine and
once widely used in China.
Fronting has been used with success since 2013
for the rendezvous component of another transport called flash proxy~\cite{flashproxy}.
GoAgent and the flash proxy rendezvous are the most direct
inspirations of this work.

We have developed domain fronting into a system called meek,
a full-fledged circumvention transport,
implemented as a pluggable transport~\cite{pt} for Tor.
meek combines fronting with an HTTP-based tunneling proxy:
upstream data are transformed into a sequence of HTTP requests,
which are fronted in order to reach a proxy server.
The server decodes the requests and feeds their payloads
into a local Tor relay.
Downstream data received from the Tor relay
are returned to the client as HTTP responses
through the same fronted channel.
meek's architecture appears in Figure~\ref{fig:architecture}.
Section~\ref{sec:architecture} describes meek's workings in detail.

>>>>

To our knowledge,
the earliest application of domain fronting to circumvention
was by GoAgent~\cite{goagent},
a tool based on App Engine and
once widely used in China.
Fronting has also been used with success since 2013
for the rendezvous component of another transport called flash proxy~\cite{flashproxy}.
GoAgent and flash proxy's rendezvous are the most direct
inspirations of this work.

We have developed domain fronting into a full-fledged circumvention system called meek,
implemented as a Tor pluggable transport~\cite{pt}.
meek combines fronting with an HTTP-based tunneling proxy:
upstream data are transformed into a sequence of HTTP requests,
which are fronted in order to reach a proxy server.
The server decodes the requests and feeds their payloads
into a local Tor relay.
Downstream data received from the Tor relay
are returned to the client as HTTP responses
through the same fronted channel.
meek's architecture appears in Figure~\ref{fig:architecture}.
Section~\ref{sec:architecture} describes its workings in detail.
